Sea level

### 2016-12-08 EU-Circle/eu-circle_case-study-4.Rmd
More material for paper58 + more scripts for EU-Circle

Scale the

>>>>

Scale the precipitation according to the indididual wet-day mean. Then take the mean of the station series to get an index of large-scale precipitation intensity.

```{r}
mu <- apply(coredata(pr.bmd),2,'wetmean')
nv <- apply(coredata(pr.bmd),1,'nv')
X <- zoo(rowMeans(t(t(pr.bmd)/mu),na.rm=TRUE),order.by=index(pr.bmd))
X[nv < 11] <- NA
X <- as.station(X,param='rain-index',unit='dimensionless',loc='Bangladesh',
                lon=mean(lon(pr.bmd)),lat=mean(lat(pr.bmd)),alt=0)
```

Examine the index:

```{r}
plot(X,new=FALSE)
```

Check the seasonality

```{r}
wheel(X,new=FALSE)
```

The long-term perspective of the rainfall intensity

```{r}
plot(annual(X,'wetmean'),new=FALSE)
grid()
lines(trend(annual(X,'wetmean')),lty=2)
```

The long-term perspective of the wet-day frequency

```{r}
plot(annual(X,'wetfreq'),new=FALSE)
grid()
lines(trend(annual(X,'wetfreq')),lty=2)
```

Get data on storm tracks... IMILAST
Correlation between storm tracks and stations.

### 2016-12-08 EU-Circle/eu-circle_case-study-SL.Rmd
More material for paper58 + more scripts for EU-Circle

@@

```{r sea-level-data}
gsl <- GSL()
gloss <- station.gcloss()
sonel <- station.sonel()
newlin <- station.newlin()
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

```{r}
dm <- function(x) {
  if (!is.null(dim(x))) y <- zoo(t(t(coredata(x)) -                      colMeans(coredata(x),na.rm=TRUE)),order.by=index(x)) else
                        y <- zoo(x - mean(x,na.rm=TRUE), order.by=index(x))
  y <- attrcp(x,y)
  class(y) <- class(x)
  y
}
```

@@

```{r sea-level-data}
gsl <- GSL()
gloss <- station.gloss()
sonel <- station.sonel()
#newlyn <- station.newlyn()
```

Examine the mean seasonal cycle in the tide gauge records:

```{r}
plot(aggregate(dm(gloss),month,'mean'),map.show=FALSE,new=FALSE)
lines(aggregate(dm(gsl),month,'mean'))

plot(aggregate(dm(sonel),month,'mean'),new=FALSE)
```

Examine globally distributed tide gauge data.

```{r, fig.height=8}
gloss <- subset(gloss,it=c(1950,1992))
nv <- apply(coredata(gloss),2,'nv')
gloss <- subset(gloss,is=nv > 400)
gloss <- pcafill(gloss)
pca <- PCA(annual(gloss))
plot(pca,new=FALSE)
```

Tide gauge data from the coast of northern France. There are some missing data gaps, but ignore those.

```{r, fig.height=8}
sonel <- annual(sonel,nmin=275)
sonel <- subset(sonel,it=c(1976,2015))
nv <- apply(coredata(sonel),2,'nv')
sonel <- subset(sonel,is=nv > 30)
sonel <- pcafill(sonel)
pca <- PCA(annual(sonel),n=3)
plot(pca,new=FALSE)
```

Connect to the global mean sea level

```{r}
gsl <- annual(gsl); index(gsl) <- year(gsl)
xy <- merge(zoo(annual(gsl)),zoo(pca),all=TRUE)
cal.sl <- data.frame(y = xy[,2],x=xy[,1])
slfit <- lm(y ~ x, data=cal.sl)
print(summary(slfit))
```

Construct the effect of a global sea level rise on the local tide levels using the leading PC only:

```{r}
z <- gsl; dim(z) <- c(length(z),1)
U <- attr(pca,'pattern')[,1]; dim(U) <- c(1,length(U))
## Need to apply the matrix product to recover the original data. 
y <- zoo((attr(pca,'eigenvalues')[1] * slfit$coefficient[2]) * (z %*% U),order.by=index(gsl))
plot(y,plot.type='single')
grid()
```

This regression model can now be applied to projected global mean sea levels from e.g. CMIP. Need to use the `slfit$coefficient[2]` together with `U`, `attr(pca,'eigenvalues')[1]` and the global sea level.
